---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rshinycox



The goal of rshinycox is to provide a tool for researchers to easily create shiny applications to display  one or more Cox model-predicted survival curves. This work was motivated by clinical research to provide an interactive summary of fitted Cox models, make it easy for researchers to generate these summaries for their own research, and to support dissemination by minimizing the use of subject-identifiable data.  

Tables of hazard ratios remain an important summary of fitted Cox models, but predicted survival curves can provide a different summary that may be more interpretable to clinicians and patients. 

While shiny apps are excellent tools for visualization, development of these apps can be challenging for unfamiliar users. This package allows a user to input their final Cox model(s) into the function `shine_coxph()` to create a shiny app for the user with minimal additional work required.  

The function `shine_coxph()` initially uses the original data for internal verification purposes, but discards the original data when the app is made, containing only the bare necessities to make predictions (predictions are made in the application using the object returned by `prep_coxfit()`). When disseminating the final app, subject-identifiable data are not distributed. 

## Installation
You can install this package using:
```r
install.packages("rshinycox")
```

You can install the development version of rshinycox from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("harryc598/rshinycox")
```

## Example

Here is an example using multiple treatment arms, which will highlight the usefulness of this package. If you move around the inputs, you can see how for different combinations, one treatment might prevail over the other.

```{r example}
library(rshinycox)
library(survival)
split_colon <- split(colon, colon$rx)

colon_arm1 <- split_colon$Obs
colon_arm2 <- split_colon$Lev
colon_arm3 <- split_colon$`Lev+5FU`

colon1ph <- coxph(Surv(time, status) ~sex +  age + obstruct + nodes, colon_arm1,
                  x = TRUE, model = TRUE)
colon2ph <- coxph(Surv(time, status) ~ sex + age + obstruct + nodes, colon_arm2,
                  x = TRUE, model = TRUE)
colon3ph <- coxph(Surv(time, status) ~ sex + age + obstruct + nodes, colon_arm3,
                  x = TRUE, model = TRUE)
# This will write a shiny app into whatever your working directory is
# shine_coxph("arm1" = colon1ph, "arm2" = colon2ph, "arm3" = colon3ph, theme = "dashboard", app.dir = getwd())

```

